More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-03-20 2016-Weak-FH-Bisim/WeakBisim.tex
simpler OTs plus other remarks during meeting

The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes transitions of several LTSs with
action of some holes, the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{def:OpenTransitions}
	An \emph{open transition} over a set  $(S_i,s_{0 i}, \rightarrow_i)^{i\in
	I}$ of LTSs, a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\inferrule*[myfraction=\reddottedrule]
	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
	{s \OTarrow {v}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and for all
        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and $\xrightarrow{b_j}_j$
        is a transition of the hole $j$, for any action $b_j$ in the
        sort $\Sort_j$. $v$ is a variable denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
	hold \emph{after the open transition}, they are represented as a substitution of the 
	form $\{x_k\gets e_k\}^{k\in K}$ 
	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
	variables of the open transition.
\end{definition}

\begin{example}\emph{An open-transition.}
  \label{OT:ABP}
  The \texttt{ABP} pNet of Fig. \ref{schema:ABP-composed} has 2 controllers and 2 holes. One of its possible open-transition is:

@@

\begin{definition}[Open automaton]
	\label{def:open-automaton}
	An \emph{open automaton} is a structure\\ $A =
	<\LTS_i^{i\in I},J,\mathcal{S},s_0,\mathcal{T}>$ where:
	\begin{itemize}
		\item[$\bullet$]  $I$ and $J$ are  sets of indices,
		\item[$\bullet$]  $\LTS_i^{i\in I}$ is a family of LTSs,
		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
		among $\mathcal{S}$,
		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
		$t\in \mathcal{T}$ there exist $I'$, $J'$ with $I'\subseteq I$, $J'
		\subseteq J$, such that $t$ is an open transition over $\LTS_i^{i\in I'}$, $J'$,
		and  $\mathcal{S}$.

@@

\begin{definition}[Operational semantics of open pNets]
	\label{def:operationalSemantics}
	The semantics of a pNet $p$ is an open automaton $A = <Leaves(p),Holes(p),States(p),InitState(p),
	\mathcal{T}>$ where $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
%	\begin{itemize}
%		\item $J$ is the set of holes: $Holes(p)= J$. 
		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
%		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
%		\item $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
%	\end{itemize}

@@

	\begin{description}
		\item[{\bf Tr1:}]
		$\inferrule
		{ s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
					J}\rangle} s'\in \to  }
		{ \mylangle  S,s_0, \to \myrangle
			\models
			\inferrule*[myfraction=\reddottedrule]
			{\{s \xrightarrow{\alpha} s'\} ,\emptyset ,
			e_b,\left\{x_j\gets e_j\right\}^{j\in J}}
			{\ostate{s} \OTarrow{\alpha} \ostate{s'}}
		}
		$\LUDO {removed a ${}_p$ that was not bound}
	\end{description}
%	Note that this note is greatly simplified by the fact that variables are local to 
%	thread; introducing global state variables or accepting loops to the same 
%	state would 
%	require to reason 
%	on the scope of 
%	each variables, and to introduce additional variables to handle the several occurence 
%	of the same pLTS variable in the predicates. Indeed the constraints on pLTS 
%	transitions 
%	ensure that the same variable never appears both on the left and on the right of the 
%	equations of a predicate.

	The second rule deals with pNet nodes: for each possible
	synchronisation vector applicable to the rule subject, the premisses
	include one {\em open transition} for each sub-pNet involved , one possible
	{\em action} for each Hole involved, and the predicate relating these
	with the resulting action of the vector. The sub-pNets involved are split between two 
	sets, $I_2$ for subnets that are pLTSs, and $I_1$ for the others.
	A key to understand this rule is that the open transitions are
	expressed in terms of the leaves and holes of the pNet structure,
	i.e. a flatten view of the pNet: e.g. $L$ is the index set of the
	Leaves, $L_m$ the index set of the leaves of one subnet indexed $m$, so all $L_m$
	are disjoint subsets of $L$. Thus the states in the open transitions,
	at each level, are tuples including states of all the
	leaves of the pNet, not only those involved in the chosen
	synchronisation vector.
	\begin{description}
		\item[{\bf Tr2:}]
	\end{description}

	\noindent
    $\inferrule
    {k\!\in\! K \\SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} \\
    	Leaves(\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
    	\forall m\!\!\in\!\! I_1. {\pNet_m \models\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \\
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} }
\\ 	
     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in (I_1\uplus I_2)},b_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
    }
    {\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $
	\medskip
%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
%            J_k},v)$ is built ? You mean more than what is written on previous page????}
	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
	%%not included in the first version... I'm unsure whether this is the best place to
	%%include it, because it may change the decidability conditions on predicates}

@@

\begin{figure}[tb]
\begin{mathpar}
  \small
  \inferrule
    {\inferrule
        {0 \xrightarrow {\delta}_{C_3} 1}
        {C_3
          \models
            \openrule{
              0 \xrightarrow {\delta}_{C_3} 1,\,
              \{\xrightarrow{\delta(x_1)}_P\},\,
              v_1=\delta(x_1)}
                      {\ostate{0}\OTarrow{v_1}\ostate{1}}
        }\\
%      \sm{fresh}v         \\
      \inferrule%*[right={L_1}]
        {
%          \sm{fresh}{a_Q} \\
          \inferrule
              {0 \xrightarrow{l}_{C_4} 0}
              % {\ostate{0}\xrightarrow{l}\ostate{0}}
              {C_4
                \models
                \openrule{
                      0 \xrightarrow l_{C_4} 0,\,
                      \sm{Pred}_{C_4}}
                      {\ostate{0}\OTarrow{l}\ostate{0}}
              }
        }
        {
          \textrm{Q>>R}\models
              \openrule
                  { 0 \xrightarrow {l}_{C_4} 0,\,
                    \{\xrightarrow{acc(x_2)}_Q\},\,
                    \ v_2=acc(x_2)
                  }
                  {\ostate{0}\OTarrow{v_2}\ostate{0}}
        }   
    }
    {
     \textrm{P>>(Q>>R)}
     \models
     \openrule
         { 0 \xrightarrow{\delta}_{C_3} 1, \\ 0 \xrightarrow{l}_{C_4} 0,\\
           \{\xrightarrow{\delta(x)}_P,\,\xrightarrow{acc(x)}_Q\}, \\
            a_3=v_1 \wedge v=a_3 \wedge x_1=x_2
           }
         {\ostate{00} \OTarrow{v} \ostate{10}}
      }\vspace{-4ex}
\end{mathpar}
  \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for ``P>>(Q>>R)''}
  \label{usingrules:OT2}
\end{figure}

@@

\noindent
\begin{minipage}{0.69\linewidth} 	Suppose that
   $A_1 = <\overline{\LTS_1},J,\mathcal{S}_1, s_0,
   \mathcal{T}_1>$ and $A_2 = <\overline{\LTS_2},J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
   are open automata where the set
   of holes are equal 
   and of the same sort.

@@

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \inferrule*[myfraction=\reddottedrule]
         {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1}, % , s_i,s'_i\in 
         %States(I_1)
           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {v} s'}

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
 \begin{mathpar}
%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
    \inferrule*[myfraction=\reddottedrule]
         {\{t_i\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{ x}},
           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTarrow {v_x} t_x}
%         \right)
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
 \mathcal{R}$; 
 and  \\
 $\Pred_{s,t} \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.

\subsection{Running example}

\TODO{Eric: full result of the tool execution on the running
  example. Full ? certainly not, just a subset...}

Let $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$ be a relation over the set $\mathcal{S}_1$ and 
$\mathcal{S}_2$ constrained by a predicate.
More precisely, for any pair $(s,t)$, there is a 
   single
      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
      if $\Pred_{s,t}$ 
      is 
      true, i.e. the states are related when the variables in $s$ and $t$ verify the 
      predicate $\Pred_{s,t}$.
 FH-bisimulation is defined formally: 
 \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim}

\noindent
\begin{minipage}{0.69\linewidth} 	Suppose that
   $A_1 = <\overline{\LTS_1},J,\mathcal{S}_1, s_0,
   \mathcal{T}_1>$ and $A_2 = <\overline{\LTS_2},J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
   are open automata where the set
   of holes are equal 
   and of the same sort.

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \inferrule*[myfraction=\reddottedrule]
         {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1}, % , s_i,s'_i\in 
         %States(I_1)
           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {v} s'}

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
 \begin{mathpar}
%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
    \inferrule*[myfraction=\reddottedrule]
         {\{t_i\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{ x}},
           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTarrow {v_x} t_x}
%         \right)
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
 \mathcal{R}$; 
 and  \\
 $\Pred_{s,t} \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.

@@

 \begin{mathpar}
 \inferrule*[myfraction=\reddottedrule]
         {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1}, 
           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred,\Post}
         {s \OTWeakarrow {v} s'}
         \in \mathcal{T}^*
 \end{mathpar}

@@

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \inferrule*[myfraction=\reddottedrule]
         {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1},
           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {v} s'}

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2^*$:
 \begin{mathpar}
    \inferrule*[myfraction=\reddottedrule]
         {\{t_i\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{x}},
           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {v_x} t_x}
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

@@

       	\inferrule*[myfraction=\reddottedrule]
       	{\{s_i\xrightarrow{a_i}_i {s}'_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in
       		%States(I_1)
       		\{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
       	{s \OTarrow {v} {s}'}

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{\{t_{p i}\xrightarrow{a_{p i x}}_i t_{p i x}\}^{i\in I_{p x}},
       		\{\xrightarrow{b_{j p x}}_j\}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
       	{t_p \OTarrow {v_{px}} t_{p x}}
       	%         \right)
       	\end{mathpar}

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{\{u_i\xrightarrow{a_{i p x y}}_i u_{i p x y}\}^{i\in I_{p x y}},
       		\{\xrightarrow{b_{j p x y}}_j\}^{j\in J_{pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{u \OTarrow {v_{pxy}} u_{pxy}}
       	%         \right)

@@

Now focus on OTs of the subnets. For each $m\in I_1\uplus I_2$ we have one of the two 
following OT\footnotemark[\thefootnote]:\\[-2ex]
\[
\pNet_m \models\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}\]
Or
\[{ \pNet_m 
    	 \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}}}\]

>>>>

The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes transitions of several LTSs with
action of some holes, the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{def:OpenTransitions}
	An \emph{open transition} over a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\inferrule*[myfraction=\reddottedrule]
	{	\{b_j\}^{j\in J}, \Pred, \Post}
	{s \OTarrow {v}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and $b_j$
        is a transition of the hole $j$, for any action $b_j$ in the
        sort $\Sort_j$. $v$ is a variable denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
	hold \emph{after the open transition}, they are represented as a substitution of the 
	form $\{x_k\gets e_k\}^{k\in K}$ 
	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
	variables of the open transition.
\end{definition}

\TODO{rewrite example with new OTs}
\begin{example}\emph{An open-transition.}
  \label{OT:ABP}
  The \texttt{ABP} pNet of Fig. \ref{schema:ABP-composed} has 2 controllers and 2 holes. One of its possible open-transition is:

@@

\begin{definition}[Open automaton]
	\label{def:open-automaton}
	An \emph{open automaton} is a structure\\ $A =
	<J,\mathcal{S},s_0,\mathcal{T}>$ where:
	\begin{itemize}
		\item[$\bullet$]   $J$ is a  set of indices,
		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
		among $\mathcal{S}$,
		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
		$t\in \mathcal{T}$ there exist  $J'$ with  $J'
		\subseteq J$, such that $t$ is an open transition over  $J'$,
		and  $\mathcal{S}$.

@@

\begin{definition}[Operational semantics of open pNets]
	\label{def:operationalSemantics}
	The semantics of a pNet $p$ is an open automaton $A = 
	<Holes(p),States(p),InitState(p),
	\mathcal{T}>$ where $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
%	\begin{itemize}
%		\item $J$ is the set of holes: $Holes(p)= J$. 
		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
%		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
%		\item $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
%	\end{itemize}

@@

	\begin{description}
		\item[{\bf Tr1:}]
		$\inferrule
		{ s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
					J}\rangle} s'\in \to  }
		{ \mylangle  S,s_0, \to \myrangle
			\models
			\inferrule*[myfraction=\reddottedrule]
			{\emptyset ,
			e_b,\left\{x_j\gets e_j\right\}^{j\in J}}
			{\ostate{s} \OTarrow{\alpha} \ostate{s'}}
		}
		$
	\end{description}
%	Note that this note is greatly simplified by the fact that variables are local to 
%	thread; introducing global state variables or accepting loops to the same 
%	state would 
%	require to reason 
%	on the scope of 
%	each variables, and to introduce additional variables to handle the several occurence 
%	of the same pLTS variable in the predicates. Indeed the constraints on pLTS 
%	transitions 
%	ensure that the same variable never appears both on the left and on the right of the 
%	equations of a predicate.

	The second rule deals with pNet nodes: for each possible
	synchronisation vector applicable to the rule subject, the premisses
	include one {\em open transition} for each sub-pNet involved , one possible
	{\em action} for each Hole involved, and the predicate relating these
	with the resulting action of the vector. The sub-pNets involved are split between two 
	sets, $I_2$ for subnets that are pLTSs, and $I_1$ for the others, $J$ is the set of 
	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{\alpha_m^{m 
	\in M}}{\alpha'}{e_b}$ is a synchronisation vector  of \pNet  then $K=M\cap 
	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus K \setminus 
	I_2$}.

	A key to understand this rule is that the open transitions are
	expressed in terms of the leaves and holes of the pNet structure,
	i.e. a flatten view of the pNet: e.g. $L$ is the index set of the
	Leaves, $L_m$ the index set of the leaves of one subnet indexed $m$, so all $L_m$
	are disjoint subsets of $L$. Thus the states in the open transitions,
	at each level, are tuples including states of all the
	leaves of the pNet, not only those involved in the chosen
	synchronisation vector.
	\begin{description}
		\item[{\bf Tr2:}]
	\end{description}

	\noindent
    $\inferrule
    {
	\forall m\!\!\in\!\! I_1. {\pNet_m \models\inferrule*[myfraction=\reddottedrule]
    	{
    	\{{b_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \qquad
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} }\\\\
\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
k\!\in\! K \qquad SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} \\
\\     	
     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in (I_1\uplus I_2)},b_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
    }
    {\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{
    		\{{b_j}\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $
	\medskip
%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
%            J_k},v)$ is built ? You mean more than what is written on previous page????}
	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
	%%not included in the first version... I'm unsure whether this is the best place to
	%%include it, because it may change the decidability conditions on predicates}

@@

\begin{figure}[tb]
\begin{mathpar}
  \small
  \inferrule
    {\inferrule
        {0 \xrightarrow {\delta}_{C_3} 1}
        {C_3
          \models
            \openrule{
              0 \xrightarrow {\delta}_{C_3} 1,\,
              \{\xrightarrow{\delta(x_1)}_P\},\,
              v_1=\delta(x_1)}
                      {\ostate{0}\OTarrow{v_1}\ostate{1}}
        }\\
%      \sm{fresh}v         \\
      \inferrule%*[right={L_1}]
        {
%          \sm{fresh}{a_Q} \\
          \inferrule
              {0 \xrightarrow{l}_{C_4} 0}
              % {\ostate{0}\xrightarrow{l}\ostate{0}}
              {C_4
                \models
                \openrule{
                      0 \xrightarrow l_{C_4} 0,\,
                      \sm{Pred}_{C_4}}
                      {\ostate{0}\OTarrow{l}\ostate{0}}
              }
        }
        {
          \textrm{Q>>R}\models
              \openrule
                  { 0 \xrightarrow {l}_{C_4} 0,\,
                    \{\xrightarrow{acc(x_2)}_Q\},\,
                    \ v_2=acc(x_2)
                  }
                  {\ostate{0}\OTarrow{v_2}\ostate{0}}
        }   
    }
    {
     \textrm{P>>(Q>>R)}
     \models
     \openrule
         { 0 \xrightarrow{\delta}_{C_3} 1, \\ 0 \xrightarrow{l}_{C_4} 0,\\
           \{\xrightarrow{\delta(x)}_P,\,\xrightarrow{acc(x)}_Q\}, \\
            a_3=v_1 \wedge v=a_3 \wedge x_1=x_2
           }
         {\ostate{00} \OTarrow{v} \ostate{10}}
      }\vspace{-4ex}
\end{mathpar}
  \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for 
  ``P>>(Q>>R)'' \TODO{remove?}}
  \label{usingrules:OT2}
\end{figure}

@@

\noindent
\begin{minipage}{0.69\linewidth} 	Suppose that
   $A_1 = <J,\mathcal{S}_1, s_0,
   \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
   are open automata where the set
   of holes are equal 
   and of the same sort.

@@

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \inferrule*[myfraction=\reddottedrule]
         {
           \{{b_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {v} s'}

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
 \begin{mathpar}
%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
    \inferrule*[myfraction=\reddottedrule]
         {
           \{{b_{j x}}\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTarrow {v_x} t_x}
%         \right)
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
 \mathcal{R}$; 
 and  \\
 $\Pred_{s,t} \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.

@@

 \begin{mathpar}
 \inferrule*[myfraction=\reddottedrule]
         {
           \{{b_j}\}^{j\in J_1},\Pred,\Post}
         {s \OTWeakarrow {v} s'}
         \in \mathcal{T}^*
 \end{mathpar}

@@

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \inferrule*[myfraction=\reddottedrule]
         {
           \{{b_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {v} s'}

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2^*$:
 \begin{mathpar}
    \inferrule*[myfraction=\reddottedrule]
         {
           \{{b_{j x}}\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {v_x} t_x}
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

@@

       	\inferrule*[myfraction=\reddottedrule]
       	{
       		\{{b_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
       	{s \OTarrow {v} {s}'}

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{
       		\{{b_{j p x}}\}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
       	{t_p \OTarrow {v_{px}} t_{p x}}
       	%         \right)
       	\end{mathpar}

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{
       		\{{b_{j p x y}}\}^{j\in J_{pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{u \OTarrow {v_{pxy}} u_{pxy}}
       	%         \right)

@@

Now focus on OTs of the subnets. For each $m\in I_1\uplus I_2$ we have one of the two 
following OT\footnotemark[\thefootnote]:\\[-2ex]
\[
\pNet_m \models\inferrule*[myfraction=\reddottedrule]
    	{
    	\{{b_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}\]
Or
\[{ \pNet_m 
    	 \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}}}\]

Only elements of $I$ are useful to assert the premise for reduction of $P$; the last 
one ensures the open transition for the pNet $Q$ (note that $Q$ is at place $j_0$, and by 
definition of the open transition 
for $P[Q]_{j_0}$, $I'_{j_0}=I\cap L_Q$, 
$L_{j_0}=L_Q$, and $J_{j_0}=	J\cap\Holes(Q)$):\\[-2ex]
	\[Q\models{\inferrule*[myfraction=\reddottedrule]
		{
			\{{b_j}\}^{j\in J\cap\Holes(Q)}, \Pred_{j_0},  
			\Post\,''}
		{\ostate{s_i^{i\in L_Q}} \OTarrow {v_{j_0}}
			\ostate{(s_i')^{\, i\in L_Q}}}
	}\]
